An analysis on outbreak management in Toronto Health Institutions from 2020 - 2022

### 2023-02-03 outputs/paper/paper.qmd
update preamble

---
title: "An analysis on outbreak management in Toronto Health Institutions from 2020 - 2022"
author: "Julie Nguyen"
date: "`r Sys.time()`"
date-format: "D MMMM YYYY"
format:
  pdf:
    documentclass: article
    papersize: a4
    geometry: margin = 1in
    mainfont: "Garamond"
    sansfont: "Garamond"
thanks: 'Code and data are available at: https://github.com/julieenguyennn/Outbreak-Management-in-Toronto-Health-Institutions'
abstract: "Outbreak management has always been one of the most important mission for healthcare institutions, not only to prevent transmissions of diseases/illnesses but also to protect public health. Especially in the COVID-19 era, outbreak response and management is considered as the top priority in healthcare institution operation. This paper discusses the outbreak management in Toronto health institutions from 2020 to 2022, as well as pointing out the relationship between healthcare setting, outbreak type and response duration."
number-sections: true
bibliography: reference.bib
execute: 
  message: false
  warning: false
  echo: false
---
```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE)

@@

  In order to answer those questions, I chose the 03 dataset that lies in the COVID-19 era - 2020, 2021, and 2022, to analyze, compare, and contrast. During the process, all the necessary libraries and packages, R package [@rpackage] tidyverse [@tidyverse], janitor [@janitor], ggplot2 [@ggplot], RColorBrewer [@RColor], and kableExtra [@kableExtra], are utilised.

>>>>

---
title: "An analysis on outbreak management in Toronto Health Institutions from 2020 - 2022"
author: "Julie Nguyen"
date: "`r Sys.time()`"
date-format: "D MMMM YYYY"
format:
  pdf:
    documentclass: article
    papersize: a4
    geometry: margin = 1in
    mainfont: "Garamond"
    sansfont: "Garamond"
thanks: 'Code and data are available at: https://github.com/julieenguyennn/Outbreak-Management-in-Toronto-Health-Institutions'
abstract: "Outbreak management has always been one of the most important mission for healthcare institutions, not only to prevent transmissions of diseases/illnesses but also to protect public health. Especially in the COVID-19 era, outbreak response and management is considered as the top priority in healthcare institution operation. This paper discusses the outbreak management in Toronto health institutions from 2020 to 2022, as well as pointing out the relationship between healthcare setting, outbreak type and response duration in order to improve the outbreak management in Toronto health institutions."
number-sections: true
bibliography: reference.bib
execute: 
  message: false
  warning: false
  echo: false
---
```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE)

@@

  In order to answer those questions, I chose the 03 dataset that lies in the COVID-19 era - 2020, 2021, and 2022, to analyze, compare, and contrast. During the process, all the necessary libraries and packages, R package [@rpackage] tidyverse [@tidyverse], janitor [@janitor], ggplot2 [@ggplot], RColorBrewer [@RColor], kableExtra [@kableExtra], and testthat [@testthat] are utilised.
